Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-28 ms/main.tex
Fix characteristic polynomial

If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda (X+Q) + XQ - YZ$; the leading eigenvalue $\lambda_1$ is the largest of them,
\begin{equation} \label{eq:eigenvalues}
  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2} \;.
\end{equation}
Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
\begin{aligned}
 \alpha_2 > 
 \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
\alpha_1 \;.
\end{aligned}
\end{equation}

>>>>

If both eigenvalues of $\mathbf{L}^*_{ex}$ are less than 1, then the equilibrium $\vec{\tilde{p}^*}$ is externally stable and allele $m$ cannot invade the population of allele $M$. 
These eigenvalues are the root of the characteristic polynomial $\lambda^2 -\lambda \frac{(X+Q)}{\bar{w}} + \frac{XQ - YZ}{\bar{w}^2}$; the leading eigenvalue $\lambda_1$ is the largest of them,
\begin{equation} \label{eq:eigenvalues}
  \lambda_1 = \frac{X+Q + \sqrt{(X+Q)^2 - 4(XQ-YZ)}}{2\bar{w}} \;.
\end{equation}
Using \emph{SymPy} \citep{Meurer2017}, a Python library for symbolic mathematics, we find that $\lambda_1 > 1$ if 
\begin{equation} \label{eq:eigenvalues_greater_than_1_condition}
\begin{aligned}
 \alpha_2 > 
 \frac{-b (T_A-T_B) \tilde{p}^* - (T_A - T_B)  + c (1-T_B)}{bT_A - b (T_A-T_B) \tilde{p}^*} = %\\
% \frac{-\frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1} - (T_A - T_B)  + c (1-T_B)}{bT_A - \frac{c(1-T_B) - b \alpha_1 T_A - (T_A - T_B)}{1-\alpha_1}} = \\
% \frac{\frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{1-\alpha_1}}{\frac{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)}{1-\alpha_1}} = \\
%  \frac{-c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)- (1-\alpha_1)(T_A - T_B)  + (1-\alpha_1)c (1-T_B)}{(1-\alpha_1)bT_A - c(1-T_B) + b \alpha_1 T_A + (T_A - T_B)} = \\
%\frac{\alpha_1 b  T_A + \alpha_1 (T_A - T_B)  - \alpha_1 c (1-T_B)}{bT_A - c(1-T_B) + (T_A - T_B)} = 
\alpha_1 \;.
\end{aligned}
\end{equation}
